{memes}: an R interface to the MEME Suite

### 2020-09-20 manuscript.Rmd
add availability section

# Future developments:
 - Additional meme suite tools
 - more data visualizations
 - better support for PSP generation
 - Better support for amino-acid sequence usage (please contact us with feature requests)

>>>>

# Results

# Availability and Future developments:
 - packge source code: `github.com/snystrom/memes`
 - documentation website: `snystrom.github.io/memes`
 - docker container: `https://hub.docker.com/r/snystrom/memes_docker`
 - singularity container: `???`

### Future Features:
 - Additional meme suite tools
 - more data visualizations
 - better support for PSP generation
 - Better support for amino-acid sequence usage (please contact us with feature requests)
